### 2013-12-26 thesis/src/chapters/chapter-5-design.tex
Thesis: figure's label change

One of the first models that ensured system adaptivity is an autonomic component, concept based on a feed-back loop, initially proposed by IBM \cite{IBM06}. Figure \ref{ch5:autonomic-component} depicts that architecture.

@@

Since designed platform operates on multiple layers, we can extend that model by using concept of a multi-hierarchical autonomic system \cite{LiWoZh05}. Figure \ref{ch5:hierarchical-autonomic-system} illustrates that hierarchy, were each level represents a different perspective on an application scaling. Using terminology characteristic to a autonomic system, first three hierarchy levels (application tuning, container, stack) are centralized and controlled by a single elasticity controller at each level, while the last inter-cloud level is a decentralized one - each cloud instance is fully independent.

>>>>

One of the first models that ensured system adaptivity is an autonomic component, concept based on a feed-back loop, initially proposed by IBM \cite{IBM06}. Figure \ref{design:autonomic-component} depicts that architecture.

@@

Since designed platform operates on multiple layers, we can extend that model by using concept of a multi-hierarchical autonomic system \cite{LiWoZh05}. Figure \ref{design:hierarchical-autonomic-system} illustrates that hierarchy, were each level represents a different perspective on an application scaling. Using terminology characteristic to a autonomic system, first three hierarchy levels (application tuning, container, stack) are centralized and controlled by a single elasticity controller at each level, while the last inter-cloud level is a decentralized one - each cloud instance is fully independent.
